---
title: "Fatality Analysis Report System Data Processing Vignette"
author: "Qinan Hu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  results = "markup"
)
```

## Package overview
This is a Vignette describing the functions in the `far` package. This also serves as an assignment for Coursera's 
"Building R Packages" course.
This package includes data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes from 2013 to 2015.
This package provides functions to read data from the raw data file, summarize the number of incidents occurred in each month in the given year, and plot the incidents on a map of requested state in a year.

## Read single dataset
The functions `make_filename()` and `fars_read()` can be used to read data files that come with this package. In `make_filename()` you can specify the year you want to read the data from (Be ware that only data from 2013, 2014 or 2015 are available).

```{r loading_packages, message = FALSE}
library(far)
library(dplyr)
library(tidyr)
library(maps)
library(graphics)
```

```{r read_data}
filename1 <- make_filename(2013)
example_data1 <- fars_read(filename1)
head(example_data1)
```

## Read month info from multiple datasets
The function `fars_read_years()` allows reading information of months from multiple years' of data at once. It will return a list of tibbles containing each year's incident month information.

```{r read_more_data}
example_data2 <- fars_read_years(c(2013, 2014))
class(example_data2)
head(example_data2[[1]])
```

## Summarize month info from multiple datasets
The function `fars_summarize_years()` allows reading information of months from multiple years' of data at once. Then it will summarize how many incidents occurred in each month in requested years. It will return a list of tibbles containing each year's incident number summary by month.

```{r summarize_years}
example_data3 <- fars_summarize_years(c(2013, 2014))
class(example_data3)
example_data3[[1]]
```

## Plot the locations of all incidents in a state in a year
The function `fars_map_state()` will read data from a single year, plot a map of the state requested (specified by `state.num` argument), and plot the locations of all the incidents happened in that state in that year.
```{r plot_map, fig.align = 'center'}
fars_map_state(18, 2014)
```
